---
title: "leaflet for shiny"
output: html_document
---

```{r setup, include=FALSE}

library(openPoznan)
library(jsonlite)
library(purrr)
library(dplyr)
library(ggplot2)
library(ggmap)
library(leaflet)
library(sp)
library(rvest)
library(opencage)
library(fuzzyjoin)
library(textclean)
library(stringdist)
```
##

Vignette for tvm function. 

- Create map using leaflet. 
```{r tvm}
 # Leaflet map with custom icon 

  TVM_example <- tvm()

  TVM_Icon <- makeIcon(iconUrl = "https://d30y9cdsu7xlg0.cloudfront.net/png/44651-200.png",
                       iconWidth = 25, 
                       iconHeight = 30,
                       iconAnchorX = 15, 
                       iconAnchorY = 25)
  
  Poznan_with_TVM2 <- leaflet() %>%
    addTiles() %>%  
    addMarkers(lat = TVM_example$Latitude, 
               lng = TVM_example$Longitude, 
               popup = TVM_example$ID,
               icon = TVM_Icon,
               clusterOptions = markerClusterOptions())
  Poznan_with_TVM2
```
Vignette for pm function. 

- Create map using leaflet. 
```{r pm}
# Leaflet map with custom icon

  PM_final <- pm()
  
  PM_Icon <- makeIcon(iconUrl = "https://image.flaticon.com/icons/svg/34/34783.svg",
                      iconWidth = 25, 
                      iconHeight = 30,
                      iconAnchorX = 15, 
                      iconAnchorY = 25)
  
  Poznan_with_PM <- leaflet() %>%
    addTiles() %>%  
    addMarkers(lat = PM_final$Latitude, 
               lng = PM_final$Longitude, 
               popup = PM_final$ID,
               icon = PM_Icon,
               clusterOptions = markerClusterOptions())
```
Vignette for stop function. 

- Create map using leaflet. 
```{r stops}
  # Leaflet map with custom icon 

  Stops_final <- stop()
  
  Stops_Icon <- icons(iconUrl = ifelse(Stops_final$Route_Type == 3,"https://d30y9cdsu7xlg0.cloudfront.net/png/19259-200.png","http://icons.iconarchive.com/icons/icons8/android/512/Transport-Tram-icon.png"),
                      iconWidth = 25, 
                      iconHeight = 30,
                      iconAnchorX = 15, 
                      iconAnchorY = 25)
  
  Poznan_with_Stops <- leaflet() %>%
    addTiles() %>%  
    addMarkers(lat = Stops_final$Latitude, 
               lng = Stops_final$Longitude, 
               popup = Stops_final$ID,
               icon = Stops_Icon[Stops_final$Route_Type],
               clusterOptions = markerClusterOptions())
  Poznan_with_Stops
```
Vignette for cesspool function. 

- Create map using leaflet. 
```{r cesspool}
 # Leaflet map with custom icon 

  Cesspool_final <- cesspool()
  
  Cesspool_Icon <- makeIcon(iconUrl = "http://cdn.onlinewebfonts.com/svg/img_537720.png",
                       iconWidth = 25, 
                       iconHeight = 30,
                       iconAnchorX = 15, 
                       iconAnchorY = 25)
  
  Poznan_with_Cesspool <- leaflet() %>%
    addTiles() %>%  
    addMarkers(lat = Cesspool_final$Latitude, 
               lng = Cesspool_final$Longitude, 
               popup = Cesspool_final$ID,
               icon = Cesspool_Icon,
               clusterOptions = markerClusterOptions())
  Poznan_with_Cesspool
```
Vignette for sw function. 

- Create map using leaflet. 
```{r sw}
  # Leaflet map with custom icon

  SW_final <- sw()
  
  SW_Icon <- makeIcon(iconUrl = "https://www.corkdrain.ie/assets/icon4.png",
                      iconWidth = 25, 
                      iconHeight = 30,
                      iconAnchorX = 15, 
                      iconAnchorY = 25)
  
  Poznan_with_SW <- leaflet() %>%
                    addTiles() %>%  
                    addMarkers(lat = SW_final$Latitude, 
                               lng = SW_final$Longitude, 
                               popup = SW_final$ID,
                               icon = SW_Icon,
                               clusterOptions = markerClusterOptions())
  Poznan_with_SW
```
Vignette for area function. 

- Create map using leaflet (first changing data type, so it is possible). 
```{r area}
#Function spatial lines => get rid of multipolygons and polygons, so we can use Leaflet

  Areas_basic_info <- area()
  Area_full_info <- area(T)
  Area_coord_id <- Area_full_info$Coords

Area_split_data = lapply(unique(Area_coord_id$ID), function(x) {
  df = as.matrix(Area_coord_id[Area_coord_id$ID == x, c("Longitude", "Latitude") ])
  polys = Polygons(list(Polygon(df)), ID = x)
  return(polys)
})

Area_data_lines = SpatialPolygons(Area_split_data)

# Leaflet map with custom icon 

labels <- sprintf("<strong>%s</strong><br/>",
                  Areas_basic_info$School_Name) %>% 
                  lapply(htmltools::HTML)

Area_leaflet_map <- leaflet() %>%
addTiles() %>%  
  addPolygons(data = Area_data_lines,
               weight = 2, 
               opacity = 1,
               dashArray = "3",
               color = "white",
               smoothFactor = 0.5,
               fillOpacity = 0.5, 
                 highlight = highlightOptions(
                 weight = 5,
                 color = "#666",
                 fillOpacity = 0.7,
                 bringToFront = TRUE),
                   label = labels,
                   labelOptions = labelOptions(
                   style = list("font-weight" = "normal", padding = "3px 8px"),
                   textsize = "15px",
                   direction = "auto"))
Area_leaflet_map
```
Vignette for parish function. 

- Create map using leaflet (first changing data type, so it is possible). 
```{r parish}
#Function spatial lines => get rid of multipolygons and polygons, so we can use Leaflet

  Parish_basic_info <- parish()
  Parish_full_info <- parish(T)
  Parish_coord_id <- Parish_full_info$Coords

Parish_split_data = lapply(unique(Parish_coord_id$ID), function(x) {
  df = as.matrix(Parish_coord_id[Parish_coord_id$ID == x, c("Longitude", "Latitude") ])
  polys = Polygons(list(Polygon(df)), ID = x)
  return(polys)
})

Parish_data_lines = SpatialPolygons(Parish_split_data)

# Leaflet map with custom icon 

labels <- sprintf("<strong>%s</strong><br/>",
                  Parish_basic_info$Parish_Name) %>% 
                  lapply(htmltools::HTML)

Parish_leaflet_map <- leaflet() %>%
addTiles() %>%  
  addPolygons(data = Parish_data_lines,
               weight = 2, 
               opacity = 1,
               dashArray = "3",
               color = "white",
               smoothFactor = 0.5,
               fillOpacity = 0.5, 
                 highlight = highlightOptions(
                 weight = 5,
                 color = "#666",
                 fillOpacity = 0.7,
                 bringToFront = TRUE),
                   label = labels,
                   labelOptions = labelOptions(
                   style = list("font-weight" = "normal", padding = "3px 8px"),
                   textsize = "15px",
                   direction = "auto"))
                           
Parish_leaflet_map
```

