---
title: "vignettes for openPoznan" 
author: "Wojciech Dopieralski" 
date: "`r Sys.Date()`" 
output: rmarkdown::html_vignette 
vignette: > 
  %\VignetteIndexEntry{Vignette Title} 
  %\VignetteEngine{knitr::rmarkdown} 
  \usepackage[utf8]{inputenc} 
---

```{r setup, include=FALSE}


#puste 




```

## R Markdown

Vignette for tvm function. 

- Create map using gg plot, and put points on Poznan map. 
- Create map using leaflet. 


```{r cars}
  # Create point map on the graph
  
  TVM_points <- geom_point(data = TVM_final,
                           aes(x= Longitude,
                               y= Latitude,
                               group=ID), colour = "blue")
  
  # Download Poznan map and put created points on it 
  
  get_poznan <- get_map(c(16.916, 52.42), zoom = 11) 
  poznan <- ggmap(get_poznan)
  
  Poznan_with_TVM <- poznan + TVM_points
  
  plot(Poznan_with_TVM)
  
  # Leaflet map with custom icon 
  
  TVM_Icon <- makeIcon(iconUrl = "https://d30y9cdsu7xlg0.cloudfront.net/png/44651-200.png",
                       iconWidth = 25, 
                       iconHeight = 30,
                       iconAnchorX = 15, 
                       iconAnchorY = 25)
  
  Poznan_with_TVM2 <- leaflet() %>%
    addTiles() %>%  
    addMarkers(lat = TVM_final$Latitude, 
               lng = TVM_final$Longitude, 
               popup = TVM_final$ID,
               icon = TVM_Icon,
               clusterOptions = markerClusterOptions())
  Poznan_with_TVM2
```

##

Vignette for pm function. 

- Create map using gg plot.
- Create map using leaflet. 


```{r pressure, echo=FALSE}
# Create point map on the graph
  
  ggplot(data = PM_final,
         aes(x= Longitude,
             y= Latitude,
             group=ID)) +
    geom_point(colour = "blue")
  
  # Leaflet map with custom icon 
  
  PM_Icon <- makeIcon(iconUrl = "https://image.flaticon.com/icons/svg/34/34783.svg",
                      iconWidth = 25, 
                      iconHeight = 30,
                      iconAnchorX = 15, 
                      iconAnchorY = 25)
  
  Poznan_with_PM <- leaflet() %>%
    addTiles() %>%  
    addMarkers(lat = PM_final$Latitude, 
               lng = PM_final$Longitude, 
               popup = PM_final$ID,
               icon = PM_Icon,
               clusterOptions = markerClusterOptions())
```


##

Vignette for stop function. 

- Create map using gg plot.
- Create map using leaflet. 



```{r}
# Create point map on the graph
  
  ggplot(data = Stops_final,
         aes(x= Longitude,
             y= Latitude,
             group=ID)) +
    geom_point(colour = "blue")
  
  # Leaflet map with custom icon 
  
  Stops_Icon <- icons(iconUrl = ifelse(Stops_final$Route_Type == 3,"https://d30y9cdsu7xlg0.cloudfront.net/png/19259-200.png","http://icons.iconarchive.com/icons/icons8/android/512/Transport-Tram-icon.png"),
                      iconWidth = 25, 
                      iconHeight = 30,
                      iconAnchorX = 15, 
                      iconAnchorY = 25)
  
  Poznan_with_Stops <- leaflet() %>%
    addTiles() %>%  
    addMarkers(lat = Stops_final$Latitude, 
               lng = Stops_final$Longitude, 
               popup = Stops_final$ID,
               icon = Stops_Icon[Stops_final$Route_Type],
               clusterOptions = markerClusterOptions())
  Poznan_with_Stops
```

Vignette for cesspool function. 

- Create map using gg plot.
- Create map using leaflet. 



```{r}
# Create point map on the graph

ggplot(data = Cesspool_Final,
       aes(x= Longitude,
           y= Latitude,
           group=ID)) +
  geom_point(colour = "blue")

 # Leaflet map with custom icon 
  
  Cesspool_Icon <- makeIcon(iconUrl = "",
                       iconWidth = 25, 
                       iconHeight = 30,
                       iconAnchorX = 15, 
                       iconAnchorY = 25)
  
  Poznan_with_Cesspool <- leaflet() %>%
    addTiles() %>%  
    addMarkers(lat = Cesspool_final$Latitude, 
               lng = Cesspool_final$Longitude, 
               popup = Cesspool_final$ID,
               icon = Cesspool_Icon,
               clusterOptions = markerClusterOptions())
  Poznan_with_Cesspool
```

Vignette for sw function. 

- Create map using gg plot.
- Create map using leaflet. 


```{r}
 # Create point map on the graph
  
  ggplot(data = SW_final,
         aes(x= Longitude,
             y= Latitude,
             group=ID)) +
    geom_point(colour = "blue")
  
  # Leaflet map with custom icon 
  
  SW_Icon <- makeIcon(iconUrl = "",
                      iconWidth = 25, 
                      iconHeight = 30,
                      iconAnchorX = 15, 
                      iconAnchorY = 25)
  
  Poznan_with_SW <- leaflet() %>%
    addTiles() %>%  
    addMarkers(lat = SW_final$Latitude, 
               lng = SW_final$Longitude, 
               popup = SW_final$ID,
               icon = SW_Icon,
               clusterOptions = markerClusterOptions())
```

Vignette for parish function. 

- Create map using gg plot.
- Create map using leaflet (first changing data type, so it is possible). 
- Geocode with opencage.
- webscrapp wiki for Church coords.
- Use functions for finding closes string, and match Church with it's Parish.



```{r}
# Create point map on the graph

ggplot(data = Parish_coord_id,
       aes(x= Longitude,
           y= Latitude,
           group=ID)) +
  geom_polygon(colour = "blue")

#Function spatial lines => get rid of multipolygons and polygons, so we can use Leaflet

Parish_split_data = lapply(unique(Parish_coord_id$ID), function(x) {
  df = as.matrix(Parish_coord_id[Parish_coord_id$ID == x, c("Longitude", "Latitude") ])
  polys = Polygons(list(Polygon(df)), ID = x)
  return(polys)
})

Parish_data_lines = SpatialPolygons(Parish_split_data)

# Leaflet map with custom icon 

labels <- sprintf("<strong>%s</strong><br/>",
                  Parish_basic_info$Parish_Name) %>% 
                  lapply(htmltools::HTML)

Parish_leaflet_map <- leaflet() %>%
addTiles() %>%  
  addPolygons(data = Parish_data_lines,
               weight = 2, 
               opacity = 1,
               dashArray = "3",
               color = "white",
               smoothFactor = 0.5,
               fillOpacity = 0.5, 
                 highlight = highlightOptions(
                 weight = 5,
                 color = "#666",
                 fillOpacity = 0.7,
                 bringToFront = TRUE),
                   label = labels,
                   labelOptions = labelOptions(
                   style = list("font-weight" = "normal", padding = "3px 8px"),
                   textsize = "15px",
                   direction = "auto"))
                           
Parish_leaflet_map

#List of Parish from city hall api 

Church <- distinct(Parish_basic_info, Parish_Name)

Church_list_df <- data.frame(Church, stringsAsFactors = FALSE)

Church_list_df$Parish_Name <- paste("Kosciol ", Church_list_df$Parish_Name)

Church_list_df$Parish_Name <- ifelse(grepl(" w ", Church_list_df$Parish_Name), 
                                Church_list_df$Parish_Name,
                                paste(Church_list_df$Parish_Name, " w Poznaniu"))

Church_list_df[sapply(Church_list_df, is.character)] <- lapply(Church_list_df[sapply(Church_list_df,is.character)], as.factor)

#Geocoding with Opencage

Church_opencage <- opencage_forward (placename = "Kościół, 
                           Pozna??,
                           Polska",
                           key =  "1883310f1dd440b1b7b48dfbabe55ff2",               
                           countrycode = "PL",
                           language = "pl",
                           limit = 100)

Church_opencage_df <- as.data.frame(Church_opencage)

Church_coords_opencage_df <- data.frame(Church_opencage_df$results.geometry.lat,
                    Church_opencage_df$results.geometry.lng,
                    Church_opencage_df$results.formatted)

#Webscrapping from wiki (for Church coords)

url <- "https://pl.wikipedia.org/wiki/Kategoria:Ko%C5%9Bcio%C5%82y_rzymskokatolickie_w_Poznaniu"

Church_wiki_list <- url %>%
  read_html %>%
  html_nodes(".mw-category ul li a") %>%
  html_text()

Church_wiki_links <- url %>%
  read_html %>%
  html_nodes(".mw-category ul li a") %>%
  html_attr("href")

Church_wiki_links <- paste("https://pl.wikipedia.org", Church_wiki_links, sep="")

Church_coord_final <- data.frame()

for(i in 1:length(Church_wiki_list)){

  church <- Church_wiki_links[i]

  long <- church %>%
    read_html %>%
    html_nodes(".infobox .geo-nondefault .geo-dms .longitude") %>%
    html_text()

  lat <- church %>%
    read_html %>%
    html_nodes(".infobox .geo-nondefault .geo-dms .latitude") %>%
    html_text()
  
  church_name <- church %>%
    read_html %>%
    html_nodes("#firstHeading") %>%
    html_text

  if(length(long) != 0 & length(lat) != 0){

    result <- data.frame(long, lat, church_name)

    Church_coord_final <- rbind(Church_coord_final, result)
  }
}

colnames(Church_coord_final) <- c("Longitude",
                                 "Latitude",
                                 "Parish_Name")

Church_coord_final$Parish_Name <- replace_non_ascii(Church_coord_final$Parish_Name)
Church_list_df$Parish_Name <- replace_non_ascii(Church_list_df$Parish_Name)

#Changing structure of church names, so iit will be possible to match them 

Church_list_df$Parish_Name <- gsub("Swietej", "sw.", Church_list_df$Parish_Name)
Church_list_df$Parish_Name <- gsub("Swietego", "sw.", Church_list_df$Parish_Name)
Church_coord_final$Parish_Name <- gsub("Swietej", "sw.", Church_coord_final$Parish_Name)
Church_coord_final$Parish_Name <- gsub("Swietego", "sw.", Church_coord_final$Parish_Name)
Church_coord_final$Parish_Name <- gsub("Bozej", "Boskiej", Church_coord_final$Parish_Name)
Church_coord_final$Parish_Name <- gsub("Bazylika", "Kosciol", Church_coord_final$Parish_Name)
Church_list_df$Parish_Name <- gsub("Bozej", "Boskiej", Church_list_df$Parish_Name)

#Modification for 1 church so it's possible to match them

Church_coord_final$Parish_Name <- gsub("archikatedralna", "", Church_coord_final$Parish_Name)
Church_coord_final$Parish_Name <- gsub("Apostolow Slowian i Patronow Europy", "", Church_coord_final$Parish_Name)
Church_coord_final$Parish_Name <- gsub("Kosciol Nawrocenia sw. Pawla Apostola", "Kosciol Nawrocenia sw. Pawla", Church_coord_final$Parish_Name)
Church_list_df$Parish_Name <- gsub("z Pietrelciny", "", Church_list_df$Parish_Name)
Church_list_df$Parish_Name <- gsub("Chojnica - Morasko", "", Church_list_df$Parish_Name)
Church_list_df$Parish_Name <- gsub("Kosciol sw. Lukasza", "Kosciol sw. Lukasza Ewangelisty", Church_list_df$Parish_Name)
Church_list_df$Parish_Name <- gsub("Kosciol Matki Odkupiciela", "Kosciol Najswietszej Maryi Panny Matki Odkupiciela", Church_list_df$Parish_Name)

removePunctWords <- function(x) {
  gsub(pattern = "\\(\\w*", "", x)
}

Church_coord_final$Parish_Name <- removePunctWords(Church_coord_final$Parish_Name)

Church_coord_final$Parish_Name <- gsub("(.*?) w .*" , "\\1" ,Church_coord_final$Parish_Name ) 
Church_list_df$Parish_Name<- gsub("(.*?) w .*" , "\\1" , Church_list_df$Parish_Name ) 

Podobienstwa <- Church_coord_final %>% 
  stringdist_right_join(Church_list_df,
                  by = "Parish_Name",
                  distance_col = NULL,
                  method = "osa")

Macierz_odl<- stringdistmatrix(Church_coord_final$Parish_Name, 
                               Church_list_df$Parish_Name, 
                               useNames = "strings",
                               method = "jw")

Macierz_df <- as.data.frame(as.table(Macierz_odl))
```

Vignette for area function. 

- Create map using gg plot.
- Create map using leaflet (first changing data type, so it is possible). 
- Webscrapp poznan site for school adressess 
- Geocode with opencage using adressess
 
```{r}
# Create point map on the graph

ggplot(data = Area_coord_id,
       aes(x= Longitude,
           y= Latitude,
           group=ID)) +
  geom_polygon(colour = "blue")

#Function spatial lines => get rid of multipolygons and polygons, so we can use Leaflet

Area_split_data = lapply(unique(Area_coord_id$ID), function(x) {
  df = as.matrix(Area_coord_id[Area_coord_id$ID == x, c("Longitude", "Latitude") ])
  polys = Polygons(list(Polygon(df)), ID = x)
  return(polys)
})

Area_data_lines = SpatialPolygons(Area_split_data)

# Leaflet map with custom icon 

labels <- sprintf("<strong>%s</strong><br/>",
                  Areas_basic_info$School_Name) %>% 
                  lapply(htmltools::HTML)

Area_leaflet_map <- leaflet() %>%
addTiles() %>%  
  addPolygons(data = Area_data_lines,
               weight = 2, 
               opacity = 1,
               dashArray = "3",
               color = "white",
               smoothFactor = 0.5,
               fillOpacity = 0.5, 
                 highlight = highlightOptions(
                 weight = 5,
                 color = "#666",
                 fillOpacity = 0.7,
                 bringToFront = TRUE),
                   label = labels,
                   labelOptions = labelOptions(
                   style = list("font-weight" = "normal", padding = "3px 8px"),
                   textsize = "15px",
                   direction = "auto"))
                           
Area_leaflet_map
               
#Geocoding with Opencage

School_opencage <- opencage_forward (placename = "Szko?a, 
                           Pozna??,
                           Polska",
                           key =  "1883310f1dd440b1b7b48dfbabe55ff2",               
                           countrycode = "PL",
                           language = "pl")

School_opencage_df <- as.data.frame(School_opencage)

School_coords_opencage_df <- data.frame(School_opencage_df$results.geometry.lat,
                    School_opencage_df$results.geometry.lng,
                    School_opencage_df$results.formatted)

#Webscrapping Poznan site for addressess of basic schools 

School_url <- "http://www.poznan.pl/mim/oswiata/szkoly-podstawowe,poi,2284,8884/"

School_list_names <- School_url %>%
  read_html %>%
  html_nodes(".object h2") %>%
  html_text() %>% as.data.frame

School_list_address_unclear <- School_url %>%
  read_html %>%
  html_nodes(".object p") %>%
  html_text() 

School_list_remove_html <- gsub("\r?\n|\r", " ", School_list_address_unclear) 
School_list_address_clear <- gsub("(.*?)Telefon.*" , "\\1" , School_list_remove_html) %>%
                             as.data.frame

School_list_finale <- cbind(School_list_names,
                            School_list_address_clear)

colnames(School_list_finale) <- c("Name", 
                                  "Address")

School_list_finale %>% mutate_if(is.factor, as.character) -> School_list_finale


School_opencage_list <- data.frame()

for (i in 1:length(School_list_finale$Address)) {

School_opencage <- opencage_forward (placename = School_list_finale$Address[i],
                           key =  "1883310f1dd440b1b7b48dfbabe55ff2",               
                           countrycode = "PL",
                           language = "pl",
                           bounds = c(15,50,19,54),
                           limit = 100) 

School_opencage_df <- as.data.frame(School_opencage)

School_coords_opencage_df <- data.frame(lat = School_opencage_df$results.geometry.lat,
                    long = School_opencage_df$results.geometry.lng,
                    name = School_opencage_df$results.formatted,
                    iter = i)

School_opencage_list <- rbind(School_opencage_list, School_coords_opencage_df)
}
```

