---
title: "Vignettes for openPoznan"
author: "Kamil Nowak"
date: "7 sierpnia 2018"
output: rmarkdown::html_vignette
vignette: >
 %\VignetteIndexEntry{Vignette Title}
 %\VignetteEngine{knitr::rmarkdown}
 \usepackage[utf8]{inputenc} 
---

```{r setup, include=FALSE}
  library(openPoznan)
  library(jsonlite)
  library(purrr)
  library(dplyr)
  library(ggplot2)
  library(ggmap)
  library(leaflet)
  library(sp)
  library(rgeos)
  library(geosphere)
  library(gmapsdistance)
  library(XML)
```

## Vignette for addresses function.

```{r}
address_example <- addresses()
head(address_example)
```

## Create map using gg plot, and put path on map.

```{r pressure, echo=FALSE}

ggplot(data = address_example, aes(x= longitude, y= latitude, group=id)) +
  geom_path()
```

## Vignette for properties_current_trade() function.

```{r}
property_cto_example <- properties_current_trade()
head(property_cto_example)

```

## Create map using gg plot, and put points on Poznan map.

```{r}
get_poznan <- get_map(c(16.916, 52.42), zoom = 11) 

poznan <- ggmap(get_poznan)
  
poznan+geom_point(data = property_cto_example,
                           aes(x= longitude,
                               y= latitude,
                               group=id) ) 
```



## Vignette for properties_for_sale function.

```{r}
property_fs_example <- properties_for_sale()
head(property_fs_example)

```

## Create map using gg plot, and put points on Poznan map.

```{r}
get_poznan <- get_map(c(16.916, 52.42), zoom = 11) 

poznan <- ggmap(get_poznan)
  
poznan+geom_point(data = property_fs_example,
                           aes(x= longitude,
                               y= latitude,
                               group=id) ) 
  


```
## Vignette for local_spatial_dev_plans_passed function.

```{r}
lsdpp_example <- local_spatial_dev_plans_passed()
head(lsdpp_example)

```

## Create map usign gg plot.
```{r}
lsdp_coord_id <- local_spatial_dev_plans_passed(basic = FALSE)
ggplot(data = lsdp_coord_id,
       aes(x= Longitude,
           y= Latitude,
           group=ID)) +
  geom_polygon(colour = "blue")
```



## Vignette for local_spatial_dev_plans_called function.
```{r}
lsdpc_example <- local_spatial_dev_plans_called()
head(lsdpc_example)

```

## Create map usign gg plot.
```{r}
lsdpc_coord_id <- local_spatial_dev_plans_called(basic = FALSE)
ggplot(data = lsdpc_coord_id,
       aes(x= Longitude,
           y= Latitude,
           group=ID)) +
  geom_polygon(colour = "blue")
```

